Arbitrary code injection in Adblock Plus

### 2023-03-30 paper/paper.tex
Copy content from google docs

\section{Background and Goals}
TODO

\section{Attack Outline}
TODO

\section{Implementation}
TODO

\section{Discussion and Limitations}
TODO

\section{Related Work}
TODO

>>>>

\section{Background and Goals}
TODO
\begin{itemize}
\item Blocking Ads extensions massive adoption.
\item Adblock filters contain a lot of lines.
\item \$rewrite rule: what it does, why is it introduced.
\item Goal 1: prove that they imply a new attack surface.
\item Goal 2: create a full working Proof of Concept.
\end{itemize}

\section{Attack Outline}
TODO
\begin{itemize}
\item Victim website: Open redirect combined with fetching and loading JS code provokes worse problems.
\item Victim user: install malicious filter list (may be updated automatically), visit victim website.
\item Attacker: control the malicious filter list.
\item Potential impact.
\end{itemize}

\section{Implementation}
TODO
\begin{itemize}
\item Recreating the environment.
\item Adblock plus version vulnerable, browser version
\item Attacker’s website.
\item Victim’s website.
\item CSP policies.
\end{itemize}

\section{Discussion and Limitations}
TODO
\begin{itemize}
\item How Google mitigated the issue.
\item How Adblock Plus defended (limits the ability of filter rules).
\item Public warnings previous the deploy of the \$rewrite feature.
\item Limitations: downgrade of browser version was needed.
\item Limitations: further analysis on other browsers.
\end{itemize}

\section{Related Work}
TODO
\begin{itemize}
\item Advertisement blocking and detection.
\end{itemize}
